Should I Airbnb My Property?

### 2017-03-09 abb_Writeup.Rmd
Cosmetic cleanup

```{r plot_pt, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='\\label{typecomp}Property Type by Tenure'}

@@

```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals', fig.lp='ltcomp'}

@@

```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure by Type'}

@@

```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents', fig.lp='rrcomp'}

@@

```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets', fig.lp='submap'}

@@

  load(paste0(fig.path, 'ltrsubplot.RData'))
  load(paste0(fig.path, 'strsubplot.RData'))
  ltrtype.map <- ltrtype.map + ylab("")

@@

```{r table_cleansummary, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'}

cc <- clean.count[,c('operation', 'str', 'ltr')]
str.count <- cumsum(c(cc$str[1], -cc$str[-1]))
ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1]))
str.cut <- c(0, str.count[-length(str.count)] - str.count[-1])
str.per <- c(0, str.cut[-1] / str.count[-length(str.count)])
ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1])
ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)])
clean.table <- data.frame(field=cc$operation,
                          strcount=str.count,
                          strcut=str.cut,
                          strper=str.per,
                          ltrcount=ltr.count,
                          ltrcut=ltr.cut,
                          ltrper=ltr.per)

rownames(clean.table) <- NULL
clean.table$field <- c('Initial Count', 'Time', 'Property Type',
                       'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo',
                       'Rates & Rents', 'Revenue', 'Location', 'Host Policy')
clean.table$strper <- 100*round(clean.table$strper, 2)
clean.table$ltrper <- 100*round(clean.table$ltrper, 2)
names(clean.table) <- c('Filter', 'Short-term', 'Cut', '% Cut',
                        'Long-term', 'Cut', '% Cut')
options(xtable.comment = FALSE)
print(xtable(clean.table, caption='Data Cleaning Summary',
       digits=0),
       include.rownames=FALSE,
       caption.placement='top')

@@

  stre <- str.data[,c('bedrooms', 'str.ext.revenue')]
  stre$tenure <- 'Short-Term (Actual)   '
  names(stre)[2] <- 'revenue'
  strp <- str.data[,c('bedrooms', 'str.pot.revenue')]
  strp$tenure <- 'Short-Term (potential)   '
  names(strp)[2] <- 'revenue'
  ltrr <- ltr.data[,c('bedrooms', 'ltr.revenue')]
  ltrr$tenure <- 'Long-Term   '
  names(ltrr)[2] <- 'revenue'
  allr <- rbind(stre, strp, ltrr)

>>>>

```{r plot_pt, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='\\label{typecomp}Property Type by Tenure'}

@@

```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='\\label{ltypecomp}Listing Type of Short-Term Rentals', fig.lp='ltcomp'}

@@

```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='\\label{bbtype}Bed and Baths by Tenure by Type'}

@@

```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents', fig.lp='rrcomp'}

@@

```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'}

@@

  load(paste0(fig.path, 'ltrsubplot.RData'))
  load(paste0(fig.path, 'strsubplot.RData'))

  ltrtype.map <- ltrtype.map + ylab("") + ggtitle('Long-Term Properties')
  strtype.map <- strtype.map + ggtitle('Short-Term Properties')

@@

```{r table_cleansummary, results="asis", comment=FALSE, message=FALSE, echo=FALSE}

 ## Extract data

  cc <- clean.count[,c('operation', 'str', 'ltr')]

 ## Sum counts and create percentages

  str.count <- cumsum(c(cc$str[1], -cc$str[-1]))
  ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1]))
  str.cut <- c(0, str.count[-length(str.count)] - str.count[-1])
  str.per <- c(0, str.cut[-1] / str.count[-length(str.count)])
  ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1])
  ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)])

 ## Compile into data.frame

  clean.table <- data.frame(field=cc$operation,
                          strcount=str.count,
                          strcut=str.cut,
                          strper=str.per,
                          ltrcount=ltr.count,
                          ltrcut=ltr.cut,
                          ltrper=ltr.per)

  ## Fix fields and names

  rownames(clean.table) <- NULL
  clean.table$field <- c('Initial Count', 'Time', 'Property Type',
                         'Listing Type', 'Bedrooms', 'Baths', 'Bed & Bath Combo',
                         'Rates & Rents', 'Revenue', 'Location', 'Host Policy')
  clean.table$strper <- 100*round(clean.table$strper, 2)
  clean.table$ltrper <- 100*round(clean.table$ltrper, 2)
  names(clean.table) <- c('Filter', 'Short-term', 'Cut', '% Cut',
                          'Long-term', 'Cut', '% Cut')

 ## Conver to xtable and print

  options(xtable.comment = FALSE)
  print(xtable(clean.table, 
               digits=0,
               caption='Data Cleaning Summary'),
       include.rownames=FALSE,
       caption.placement='top')

@@

  stra.rev <- str.data[,c('bedrooms', 'str.ext.revenue')]
  stra.rev$tenure <- 'Short-Term (Actual)   '
  names(stra.rev)[2] <- 'revenue'
  strp.rev <- str.data[,c('bedrooms', 'str.pot.revenue')]
  strp.rev$tenure <- 'Short-Term (potential)   '
  names(strp.rev)[2] <- 'revenue'
  ltr.rev <- ltr.data[,c('bedrooms', 'ltr.revenue')]
  ltr.rev$tenure <- 'Long-Term   '
  names(ltr.rev)[2] <- 'revenue'
  revdens.data <- rbind(stra.rev, strp.rev, ltrrev)
